### 2021-11-18 input/implementation.tex
reorganize

>>>>

\TODO{To assign and maintain \processes to their best partition according to
replica creations and removals, as well as dynamic infrastructure
changes, we designed and implemented \NAME.  \NAME stands for
\underline{A}daptive \underline{S}coped broad\underline{cast}. It
relies on a primitive that allows a \process to broadcast a message
within a limited scope. We first use this primitive to guarantee
consistent partitioning when a \process can only create a new replica
within the system. We highlight the issue when a \process can also
destroy a replica, and provide a second algorithm that handles replica
removals as well as dynamic changes of the infrastructure. Finally, we
propose \NAMEC that improves \NAME by leveraging the network topology
to further reduce generated traffic at the Edge.  This section
describes the communication primitive called scoped broadcast, then
discusses the properties that guarantee consistent partitioning, and
finally details our implementation \NAME.}

### 2021-11-18 input/proposal.tex
reorganize

To assign and maintain \processes to their best partition according to
replica creations and removals, as well as dynamic infrastructure
changes, we designed and implemented \NAME.  \NAME stands for
\underline{A}daptive \underline{S}coped broad\underline{cast}. It
relies on a primitive that allows a \process to broadcast a message
within a limited scope. We first use this primitive to guarantee
consistent partitioning when a \process can only create a new replica
within the system. We highlight the issue when a \process can also
destroy a replica, and provide a second algorithm that handles replica
removals as well as dynamic changes of the infrastructure.  This
section describes the communication primitive called scoped broadcast,
then discusses the properties that guarantee consistent partitioning,
and finally details our implementation \NAME.
% and the analysis of its complexity.

@@

%For instance, a \process from Paris could scoped broadcast messages to
%all \processes in Paris; and \processes from other cities would never
%deliver such messages.
%Scoped broadcast only targets a connected \emph{subset} of \processes
%in the whole distributed system.
%

% \TODO{dynamic graph: superscript with $t$?}
In this paper, we consider Edge infrastructures with heterogeneous
\nodes interconnected by communication links. \Processes involved in
the management of content may crash but are not byzantine.  \Processes
can reliably communicate through asynchronous message passing to other
known \processes called neighbors.  % A more formal
%definition of our system is given below:
We define scoped broadcast as a communication primitive that
propagates a message around its broadcaster within an
application-dependant scope.

\begin{definition}[Edge infrastructure]
  An Edge infrastructure is a connected \underline{g}raph $G(V, E)$ of
  \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
  \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from
  \Process~$i$ to \Process~$j$ is a sequence of vertices $[i, k_1,
    k_2, \ldots k_n, j]$ with $\forall m: 0\leq m \leq n, \langle
  \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in E$.
\end{definition}

%Using epidemic
%propagation (or gossiping), \processes can reliably broadcast messages
%by forwarding delivered messages from neighbors to
%neighbors~\cite{birman1999bimodal, hadzilacos1994modular,
%  nedelec2018causal, raynal2013distributed}.
%
%However, uniform reliable
%broadcast states that \emph{all} correct \processes must deliver all
%broadcast messages. This proves costly in large scale systems
%comprising thousands of \processes. Instead, we define \emph{scoped
%broadcast} where messages reach only an application-dependant subset
%of connected \processes, thus significantly reducing the generated
%traffic of broadcast.

@@

>>>>

To provide lazy and dynamic logical partitioning in dynamic networks
using scoped broadcast, all live \processes must collaborate to
disseminate messages that notify new or removed sources to all and
only interested \processes. This section reviews step-by-step the
properties that allow \processes to converge to the desired state
together. It first defines scoped broadcast, then uses it to guarantee
consistent partitioning when a \process can only become a new source
in the system. It highlights the issue when a \process can also remove
its status of source. It shows that using local knowledge and scoped
broadcast, \processes can still reach dynamic consistent partitioning
when they are able to detect possible blocking conditions in the
dissemination of required notifications. Finally, it further constrain
the system by allowing only subsets of \processes to reach lazy
consistent partitioning. \TODO{It shows that it only needs what?}

@@

In this paper, we consider Edge infrastructures as a set of
interconnected autonomous systems comprising heterogeneous \nodes
interconnected by communication links. \Processes involved in the
management of content may crash but are not byzantine.  \Processes can
reliably communicate through asynchronous message passing to other
known \processes called neighbors.  We define scoped broadcast as a
communication primitive that propagates a message around its
broadcaster within an application-dependant scope.

\begin{definition}[Autonomous systems]
  An autonomous system is a network comprising nodes and communication
  links that we represent as a \underline{g}raph of
  \underline{v}ertices and \underline{e}dges: $G = \langle V, E
  \rangle$ with $E \in V \times V$. A \underline{p}ath $\pi_{ij}$ from
  \Process~$i$ to \Process~$j$ is a sequence of vertices $[i, k_1,
    k_2, \ldots k_n, j]$ with $\forall m: 0\leq m \leq n, \langle
  \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in E$.
\end{definition}

%% \begin{definition}[Edge infrastructure]
%%   An Edge infrastructure is a connected \underline{g}raph $G(V, E)$ of
%%   \underline{v}ertices $V$ and bidirectional \underline{e}dges $E
%%   \subseteq V \times V$.  A \underline{p}ath $\pi_{ij}$ from
%%   \Process~$i$ to \Process~$j$ is a sequence of vertices $[i, k_1,
%%     k_2, \ldots k_n, j]$ with $\forall m: 0\leq m \leq n, \langle
%%   \pi_{ij}[m], \pi_{ij}[m+1] \rangle \in E$.
%% \end{definition}

@@

Edge infrastructures are networks of networks. \TODO{Meow.}

\begin{definition}[Edge infrastructure]
  An Edge infrastructure $\mathcal{G}$ has multiple autonomous systems
  interconnected with additional links $\mathcal{E} \in V_1 \times
  V_2$ where $V_1 \neq V_2$, hence $\mathcal{G} = \langle \{G_1,
  \ldots G_n\}, \mathcal{E} \rangle$.
\end{definition}
